```{r,  echo = FALSE}
library(lpSolveAPI)
setwd('C:\\Users\\ganga020\\Google Drive\\Ed Research\\Heterogenous treatment effects\\LP Final')
```


Benefit(Treatment effect) matrix for all users, I have users as row indices and treatments as column indices

```{r}
alt_ben <- read.csv('./files/alt_output.csv')
equi_ben <- read.csv('C:\\Users\\ganga020\\Google Drive\\Ed Research\\Heterogenous treatment effects\\LP\\equi_output.csv')
ego_ben <- read.csv('C:\\Users\\ganga020\\Google Drive\\Ed Research\\Heterogenous treatment effects\\LP\\ego_output.csv')

alt_ben <- alt_ben %>% select(alt_output)
equi_ben <- equi_ben %>% select(equi_output)
ego_ben <- ego_ben %>% select(ego_output)

benefit_m <- as.matrix(cbind(alt_ben, equi_ben, ego_ben))
```

Cost of treatment matrix
```{r}

alt_cost <- read.csv('C:\\Users\\ganga020\\Google Drive\\Ed Research\\Heterogenous treatment effects\\LP\\alt_c_output.csv')
equi_cost <- read.csv('C:\\Users\\ganga020\\Google Drive\\Ed Research\\Heterogenous treatment effects\\LP\\equi_c_output.csv')
ego_cost <- read.csv('C:\\Users\\ganga020\\Google Drive\\Ed Research\\Heterogenous treatment effects\\LP\\ego_c_output.csv')

alt_cost <- alt_cost %>% select(alt_c_output)
equi_cost <- equi_cost %>% select(equi_c_output)
ego_cost <- ego_cost %>% select(ego_c_output)

cost_m <- as.matrix(cbind(alt_cost, equi_cost, ego_cost))
```




Total no. of possible treatments
```{r}
n_treatments <- 3
```

Total no of users
```{r}
n_users <- nrow(benefit_m)
```

Total no of decisions to be made, which user should be assigned to which treatment
```{r}
n_decisions <- n_users*n_treatments
```

Total available budget
```{r}
budget <- 100
```



Calculating total utility. Here I am considering the utility as total benefit-total cost
```{r}
utility_m <- benefit_m - cost_m
utility_v <- c(utility_m)
head(utility_m)
```

Initializing the linear programming function
```{r}
lprec<-make.lp(0,n_decisions)
```

Initializing the objective function
The objective function here is the maximization of (total benefit - total cost) i.e. total utility
```{r}
set.objfn(lprec, utility_v)
```

Adding constarints
1: Each user can be assigned to only one treatment.
2. Total cost cannot exceed budget.
3. Each user can only be assigned to one treatment only once


Adding constraint 1
1: Each user can be assigned to maximum one treatment.
```{r}
rep.col<-function(x,n){
  matrix(rep(x,each=n), ncol=n, byrow=TRUE)
}
I <- diag(n_users)
for(i in 1:n_users){
  add.constraint(lprec, c(rep.col(I[,i],n_treatments)), "<=", 1)
}
```

Adding constraint 2
2. Total cost cannot exceed budget.
```{r}
add.constraint(lprec, c(cost_m), "<=", budget)
```

Adding constraint 3
3. set the type of decision variables to binary
```{r}
set.type(lprec,1:n_decisions,"binary")
```

set the LP solver preference to maximization (instead of minimization)
```{r}
lp.control(lprec,sense='max')
```

Visually check the model, write the model to a text file
```{r}
write.lp(lprec,'lpmodel2.txt',type='lp')
```

solve the model
The output '0' means that there is a solution
```{r}
solve(lprec)
```

# Final result
This matrix shows which user is allocated what treatment under the set constraints 
We can see that many users are not allocated any treatment because of constrained budget.
```{r}
matrix(get.variables(lprec),nrow=n_users)
```


save the results in a csv
```{r}
write.csv(matrix(get.variables(lprec),nrow=n_users),"solution.csv")
```

